Presentation Title

### 2017-06-12 thesis/chapters/ch2-model.tex
Give structure

\subsubsection*{Asynchronous common subset}
TODO give history/background of ACS
Asynchronous common subset (ACS) is an especially useful primitive for blockchain systems.
It allows any party to propose a value and the result is the set union of all the proposed values by the majority.
Concretely, ACS needs to satisfy the following properties (adapted from~\cite{miller2016honey}).
\begin{enumerate}
    \item \emph{Validity}:
        If any correct party outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ parties.
    \item \emph{Agreement}:
        If a correct party outputs $C$, then every party outputs $C$.
    \item \emph{Totality}:
        If $n - f$ party receive an input, then all correct parties produce an output.
\end{enumerate}

@@

We assume a distributed network where nodes are fully connected,
the channels are reliable\footnote{
    Reliability can be achieved in unreliable networks by resending messages or using some error correction code.
},
but messages may be re-ordered and delayed by at most some time $\Delta$,
this is sometimes known as a $\Delta$-synchronous network.
Nodes are identified by their public key thus we assume there exist a Public Key Infrastructure (PKI).
In addition, we assume the existance of cryptographically secure hash function $\textsf{H}(\cdot)$,
that has preimage resistance, second preimage resistance and collision resistance.

@@

\emph{Agreed enclosure} is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.
Similarly, \emph{agreed fragment} is computed using agreed enclosure.
We define its function to be $\textsf{agreed\_fragment}(\cdot)$

@@

TODO agreed fragment must be consecutive

@@

Our consensus protocol runs on top of the model described above.
It is directly related to the creation of CP blocks.
The objectives of the protocol are to allow honest nodes always make progress (by creating new CP blocks),
the consensus result in every round should be correct and the facilitators election should be unbiased.
Concretely, we define the necessary properties as follows.
\begin{definition}
\label{def:consensus}
\textbf{\emph{Necessary properties of the consensus protocol}}

For any $r \in \{ x \in \mathbb{Z}_+ : x < \infty \}$, starting at the genesis round (round 0),
the system will eventually reach $r$\textsuperscript{th} round.
Further, for every non-genesis round $r$ ($r > 0$), the following properties must be satisfied.
\begin{enumerate}
    \item \emph{Fair lottery}:
        Every node with a CP block in $\C_{r - 1}$,
        should have an equal probability to be elected as a facilitator in round $r$.
    \item \emph{Consistent facilitators}:
        If one honest node decides on a list of facilitators in round $r$,
        every other node honest decides on the same list.
    \item \emph{Validity}:
        If any correct facilitator outputs a set $C$, then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ facilitators.
        Note that the input is a set of CP blocks, so the output is a set of a set of CP blocks.
    \item \emph{Agreement}:
        If a correct facilitator outputs $C$, then every facilitator outputs $C$.
    \item \emph{Totality}:
        If $n - f$ facilitators receive an input, then all correct facilitators produce an output.
\end{enumerate}
\end{definition}
Note that the final three properties are on the facilitators rather than on every node,
they are the properties ACS. 
The fair lottery and consistent facilitator are properties on every node,
they are prerequites for ACS.

@@

Our bootstrap phase runs as follows.
First we assume all $N$ nodes start simultaneously.
The facilitators for round 0 are hard coded in the program.
In practice this could be the machines controlled by the developer.
If some node $u$ is not a facilitator,
it sends the message $\langle \texttt{cp\_msg}, c_{u, 0} \rangle$ to all the facilitators.
If $u$ is a facilitator, it does the same, but also waits for some time $\Delta + 1$ to collect messages of type \texttt{cp\_msg}.
After $\Delta + 1$ elapses, it begins the atomic broadcast protocol using the collected CP blocks as the proposal.
$\C_0$ is agreed at the end of the protocol.
This concludes the bootstrap phase.

The bootstrap phase can be seen as an idealised version of the setup phase combined with the consensus phase,
which we describe next.

\subsection{Setup phase}
The setup phase begins immediately after some consensus result is agreed, but not yet disseminate.
This could be right after the bootstrap phase.
The goal is to reach agreement on a list of new facilitators between every node
and should correspond to the fair lottery and consistent facilitators in \Cref{def:consensus}.

The setup phase works as follows.
Assume that facilitators of round $r-1$ have just agreed on $\C_{r-1}$.
They then immediately broadcast two messages to all the nodes---
first the consensus message $\langle \texttt{cons\_msg}, \C_{r-1} \rangle$,
and second the signature message $\langle \texttt{cons\_sig}, r, sig \rangle$.
The reason for sending \texttt{cons\_sig} is the following.
Recall that channels are not authenticated, 
and there are no signatures in $\C_{r - 1}$.
If a non-facilitator sees some $\C_{r - 1}$, it cannot immediately trust it because it may have been forged.
Thus, To guarantee authenticity, every facilitator sends an additional message that is the signature of $\C_r$.

Continuing, upon receiving $\C_{r - 1}$ and at least $t + 1$ valid signatures by $u$, $u$ performs two asks.
First, it computes the new facilitators using $\textsf{get\_facilitator}(C, n)$ (\Cref{alg:facilitator})
and updates its facilitator list to the result.
Second, it creates a new CP block using $\textsf{new\_cp}(\C_{r - 1}, r - 1)$ (\Cref{alg:new-cp}).
This concludes the setup phase.

\begin{algorithm}
\caption{Function $\textsf{get\_facilitator}(C, n)$ takes a list of CP blocks $C$ and an integer $n$,
sort evey element in $C$ by its luck value (the $\lambda$-expression), and outputs the smallest $n$ elements.}
\label{alg:facilitator}
\begin{algorithmic}
\State $\textbf{take} (n, \textbf{sort} (\textbf{map}(\lambda x.\textsf{H}(x || pk \text{ of } x), C)))$
\end{algorithmic}
\end{algorithm}

@@

\subsection{Consensus Phase}
The consensus phase begins after the new facilitators are selected.
Assuming the facilitators are of round $r$,
the goal is to agree on some $\C_r$ between the facilitators.
There are two scenarios in the consensus phase.
First, if node $u$ is not the facilitator, it sends $\langle \texttt{cp\_msg}, c_{u, h} \rangle$ to all the facilitators.
Second if the node is a facilitator, it waits for some duration $D$ and collect messages of type \texttt{cp\_msg}, where $D \gg \Delta$.
After $D$ is elapsed, it begins the ACS protocol and some $\C_r$ should be agreed upon by the end of it.
The facilitators must satisfy the validity, agreement and totality properties from \Cref{def:consensus}.
This bring us back to the setup phase and the cycle can be started again.

We remark that this procedure is the same as what is described in the bootstrap phase (\Cref{sec:bootstrap}),
but the precondition and the waiting time is different.
In particular, the bootstrap stage assumed that every node initiated and sent the \texttt{cp\_msg} simultaneously,
but here we make no such assumption.
Furthermore, in the bootstrap phase nodes wait for duration $\Delta + 1$ to collect all the CP blocks,
here we wait for some duration $D$---a system parameter,
which is much larger than $\Delta + 1$ to ensure that all honest \texttt{cp\_msg} are collected.

@@

\begin{algorithm}
\caption{Function $\textsf{get\_validity}(t_{u, i}, F_{v, j})$ runs in the private context of $u$.
$t_{u, i}$ is the transaction that $u$ wishes to verify, and $F_{v, j}$ is the corresponding fragment received from $v$.}
\label{alg:get-validity}

@@

    \State $F_{u, i} \gets \textsf{agreed\_fragment}(t_{u, i})$
    \If{$F_{u, i} = \bot$}
        \State \Return \emph{unknown}
    \EndIf \Comment $u$ has agreed fragment
    \State

@@

\subsection{Validation Protocol}
With the validity definition, we are ready to construct a protocol for determining the validity of transactions.
The protocol is a simple response and request protocol (\Cref{alg:vd-proto}).
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\begin{enumerate}
    \item \emph{Correctness}:
        The validation protocol outputs the correct result
        according to the aforementioned validity definition.
    \item \emph{Agreement}:
        If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
        then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
    \item \emph{Liveness}:
        Any valid transactions can be validated eventually.
    \item \emph{Unforgeability}:
        If some transaction is valid, it cannot be forged into an invalid transaction.
        If some transaction is invalid, it cannot be forged into a valid transaction.
\end{enumerate}
\end{definition}

@@

>>>>

\subsubsection*{Asynchronous common subset}
TODO give history/background of ACS
Asynchronous common subset (ACS) is an especially useful primitive for blockchain systems.
It allows any party to propose a value and the result is the set union of all the proposed values by the majority.
Concretely, ACS needs to satisfy the following properties (adapted from~\cite{miller2016honey}).
\begin{definition}
\label{def:acs}
\textbf{\emph{Properties of ACS}}

\begin{enumerate}
    \item \emph{Validity}:
        If any correct party outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ parties.
    \item \emph{Agreement}:
        If a correct party outputs $C$, then every party outputs $C$.
    \item \emph{Totality}:
        If $n - f$ party receive an input, then all correct parties produce an output.
\end{enumerate}
\end{definition}

@@

We assume a distributed network where nodes are fully connected,
the channels are reliable\footnote{
    Reliability can be achieved in unreliable networks by resending messages or using some error correction code.
},
but messages may be re-ordered and delayed by at most some time $\Delta$,
this is sometimes known as a $\Delta$-synchronous network.
We assume there exist a Public Key Infrastructure (PKI), and nodes are identified by their unique and permanent public key.
Finally, we use the random oracle model, i.e. calls to the random oracle are denoted by $\textsf{H}(\cdot)$.

@@

\emph{Agreed enclosure} is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$ and also must be the smallest enclosure.
That is, suppose a chain is in the form
    $\{c_{i}, c_{i+1}, t_{i+2}, c_{i+3}\}$\footnote{Usually the notation is of the form $c_{u, i}$, but the node identity is not important here so we simplify it to $c_{i}$}
    and $c_{i}, c_{i+1}, c_{i+3}$ are in $\C_r, \C_{r+1}, \C_{r+3}$ respectively,
    then the agreed enclosure of $t_{i+2}$ is $\langle c_{i+1}, c_{i+3}\rangle$ and cannot be $\langle c_{i}, c_{i+3}\rangle$.
Similarly, \emph{agreed fragment} is computed using the agreed enclosure.
We define its function to be $\textsf{agreed\_fragment}(\cdot)$

@@

@@

Our consensus protocol runs on top of the model described above.
It is directly related to the creation of CP blocks.
The objectives of the protocol are to
    allow honest nodes always make progress (by creating new CP blocks),
    compute correct consensus result in every round
    and have unbiased election of facilitators.
Concretely, we define the necessary properties as follows,
it is collectively known as the correctness properties of the consensus protocol.
\begin{definition}
\label{def:consensus}
\textbf{\emph{Correctness properties of the consensus protocol}}

$\forall r \in \mathbb{N}$, the following properties must be satisfied.
\begin{enumerate}
    \item \emph{Agreement}:
        If one honest node outputs a list of facilitators $\F_r$,
        every other node honest decides on $\F_r$
    \item \emph{Validity}:
        If any honest node outputs $\F_r$, then $|\F_r| > n$ and $|\F_r|$ must contain at least $n - t$ honest nodes.
    \item \emph{Fairness}:
        Every node should have an equal probability of becoming a facilitator.
    \item \emph{Termination}:
        At the end of the round, every node outputs some $\F_r$.
\end{enumerate}

\end{definition}
Note that the final three properties are on the facilitators rather than on every node,
they are the properties ACS. 
The fair lottery and consistent facilitator are properties on every node,
they are prerequites for ACS.

@@

Imagine that there is some bootstrap oracle, that initiates the code on every node.
The code satisfied all the properties in \Cref{def:consensus}.
Namely every node has the same set of valid facilitators $\F_1$ that are randomly choosen.
This concludes the bootstrap phase.

In practice, the bootstrap oracle is most likely the software developer and some of the desired properties cannot be achieved.
In particular, it is not possible to have the fairness property because it is unlikely that the developer knows the identity of every node in advance.

\subsection{Consensus Phase}
\label{sec:consensus-phase}
The consensus phase begins when $\F_r$ is available to all the nodes.
Note that $\F_r$ indicates the facilitators that were elected using result of round $r$ and are responsible for driving the ACS protocol in round $r + 1$.
The goal is to reach agreement on a set of new facilitators $\F_{r + 1}$ that satisfied \Cref{def:consensus}.

There are two scenarios in the consensus phase.
First, if node $u$ is not the facilitator, it sends $\langle \texttt{cp\_msg}, c_{u, h} \rangle$ to all the facilitators.
Second if the node is a facilitator, it waits for some duration $D$ and collect messages of type \texttt{cp\_msg}, where $D \gg \Delta$.
Invalid messages are removed, namely blocks with invalid signatures and duplicate blocks signed by the same key.
After $D$ elapses, it begins the ACS protocol and some $\C_{r + 1}$ should be agreed upon by the end of it.

When $\F_{r}$ reaches agreement on $\C_{r+1}$,
they immediately broadcast two messages to all the nodes---
first the consensus message $\langle \texttt{cons\_msg}, \C_{r+1} \rangle$,
and second the signature message $\langle \texttt{cons\_sig}, r, sig \rangle$.
The reason for sending \texttt{cons\_sig} is the following.
Recall that channels are not authenticated, 
and there are no signatures in $\C_{r - 1}$.
If a non-facilitator sees some $\C_{r - 1}$, it cannot immediately trust it because it may have been forged.
Thus, To guarantee authenticity, every facilitator sends an additional message that is the signature of $\C_{r + 1}$.

Continuing, upon receiving $\C_{r + 1}$ and at least $n - f$ valid signatures by some $u$, $u$ performs two asks.
First, it creates a new CP block using $\textsf{new\_cp}(\C_{r + 1}, r + 1)$ (\Cref{alg:new-cp}).
Second, it computes the new facilitators using $\textsf{get\_facilitator}(C, n)$ (\Cref{alg:facilitator})
and updates its facilitator list to the result.
This concludes the consensus phase and brings us back to the beginning of the consensus phase.

\begin{algorithm}
\caption{Function $\textsf{get\_facilitator}(C, n)$ takes a list of CP blocks $C$ and an integer $n$,
sort evey element in $C$ by its luck value (the $\lambda$-expression), and outputs the smallest $n$ elements.}
\label{alg:facilitator}
\begin{algorithmic}
\State $\textsf{take} (n, \textsf{sort\_by} (\lambda x.\textsf{H}(x || pk \text{ of } x), C))$
\end{algorithmic}
\end{algorithm}

@@

@@

TODO make $w$ the verified of some TX between $u$ and $v$.
TODO remark that $w$ calls the function.

\begin{algorithm}
\caption{Function $\textsf{get\_validity}(t_{u, i}, F_{v, j})$ validates the transaction $t_{u, i}$.
$F_{v, j}$ is the corresponding fragment received from $v$.}
We assume there exist a valid $F_{u, i}$, namely the agreed fragment of $t_{u, i}$. 
The caller is $w$, it may be $u$ but this is not necessary.
\label{alg:get-validity}

@@

    % \State $F_{u, i} \gets \textsf{agreed\_fragment}(t_{u, i})$
    % \If{$F_{u, i} = \bot$}
    %     \State \Return \emph{unknown}
    % \EndIf \Comment $u$ has agreed fragment
    % \State

@@

\subsection{Validation Protocol}
With the validity definition, we are ready to construct a protocol for determining the validity of transactions.
The protocol is a simple response and request protocol (\Cref{alg:vd-proto}).
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Implicit consensus on transactions}}

\begin{enumerate}
    \item \emph{Correctness}:
        The validation protocol outputs the correct result
        according to the aforementioned validity definition.
    \item \emph{Agreement}:
        If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
        then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
    \item \emph{Liveness}:
        Any valid transactions can be validated eventually.
    \item \emph{Unforgeability}:
        If some transaction is valid, it cannot be forged into an invalid transaction.
        If some transaction is invalid, it cannot be forged into a valid transaction.
\end{enumerate}
\end{definition}

@@

Sybil?

### 2017-06-12 thesis/chapters/ch3-analysis.tex
Give structure

\textbf{\emph{Correctness of consensus}}

$\forall r \in \mathbb{N}$, the following properties must be satisfied.
\begin{enumerate}
    \item \emph{Agreement}:
        If one honest node outputs a list of facilitators $F_r$,
        every other node honest decides on $F_r$
    \item \emph{Validity}:
        If any honest node outputs $F_r$, then $|F_r| > n$ and $|F_r|$ must contain at least $n - t$ honest nodes.
    \item \emph{Fairness}:
        Every node should have an equal probability of becoming a facilitator.
    \item \emph{Termination}:
        At the end of the round, every node outputs some $F_r$.
\end{enumerate}

@@

In the base case, agreement, validity fairness and termination follows directly from the bootstrap protocol, due to the bootstrap oracle.
Note that the result is $F_1$, which indicates the facilitators that are agreed in round 1 and are responsible for driving the ACS protocol in round 2.

For the inductive step, we assume that the properties hold for round $r$.
Then, to start round $r + 1$, the honest nodes begin sending CP blocks to $F_r$. % TODO but they don't send at the same time!
Since the honest region in $F_r$ waits for $D$ and $D \gg \Delta$,
the CP blocks of the honest nodes are guaranteed to be received by at least $n - t$ facilitators.
The agreement property of ACS (from \Cref{def:acs}) ensures that the consensus result $\C_{r + 1}$ is in consensus. 
The validity property of ACS ensures that $\C_{r + 1}$ contains the input of at least $n - 2t$ parties, but this is a quorum containing at least one honest facilitator,
thus $\C_{r + 1}$ contains the CP blocks of all facilitators.
Observe that $F_{r + 1}$ is computed using the deterministic function $\textsf{get\_facilitators}(\cdot)$.
Thus agreement of $F_{r + 1}$ follows directly from agreement of ACS.
Due to the assumption that the adversary cannot corrupt more than $t$ nodes,
validity of $F_{r + 1}$ also follows from validity of ACS.
The fairness property follows from \Cref{lemma:fairness}.
Finally, the termination property holds because $D$ eventually elapses and then ACS eventually terminates.
This completes our proof.

>>>>

@@

In the base case, agreement, validity fairness and termination follows directly from the bootstrap protocol, due to the bootstrap oracle.
Note that the result is $\F_1$, which indicates the facilitators that are agreed in round 1 and are responsible for driving the ACS protocol in round 2.

For the inductive step, we assume that the properties hold for round $r$.
Then, to start round $r + 1$, the honest nodes begin sending CP blocks to $\F_r$. % TODO but they don't send at the same time!
Since the honest region in $\F_r$ waits for $D$ and $D \gg \Delta$,
the CP blocks of the honest nodes are guaranteed to be received by at least $n - t$ facilitators.
The agreement property of ACS (from \Cref{def:acs}) ensures that the consensus result $\C_{r + 1}$ is in consensus. 
The validity property of ACS ensures that $\C_{r + 1}$ contains the input of at least $n - 2t$ parties, but this is a quorum containing at least one honest facilitator,
thus $\C_{r + 1}$ contains the CP blocks of all facilitators.
Observe that $\F_{r + 1}$ is computed using the deterministic function $\textsf{get\_facilitators}(\cdot)$.
Thus agreement of $\F_{r + 1}$ follows directly from agreement of ACS.
Due to the assumption that the adversary cannot corrupt more than $t$ nodes,
validity of $\F_{r + 1}$ also follows from validity of ACS.
The fairness property follows from \Cref{lemma:fairness}.
Finally, the termination property holds because $D$ eventually elapses and then ACS eventually terminates.
This completes our proof.
